

```{r setup, include=FALSE}
#| include: false

library(tidyverse)
```

# Abstract {.unnumbered}


Here is where we will put the abstract.

<!-- BJ !-->
Features of Quarto:



## How we should write this report

-   See @karkkainenfairface , that is an example on how to cite a bibliography.
-   Sections/title headings are automatically numbered.
-   Any changes you make, make sure to make a comment of your initials at the top of your work (INCLUDING written text) like so:

```
<!-- BJ !-->
Blah blah etc ....

OR
#BJ
r_var <- ...
```

-   Make sure to add a unique name to all code cells, and to also enable the following  (the quarto way) (In order for a figure to be cross-referenceable, its label must start with the fig- prefix):

```{r}
#| label: fig-sec1-unique-name
#| fig-cap: A caption for generated figure

ggplot() + 
  geom_line(aes(x=1:10, y = (1:10)^2))
```

- You can then refer to figures like this `@fig-sec1-unique-name` @fig-sec1-unique-name

- Format tables doing the following [Link here](https://quarto.org/docs/reference/cells/cells-knitr.html#tables)

- Do all your r work initially in your own custom `.rmd` file in this directory, so that it can be copy-pasted over later into the appropriate section (written descriptions/words can go straight into the `.qmd` files though). For example, Bhav's work is in `5000-final/BJ_work.rmd`.


::: callout-note
## From the report requirements

A 3-5 summary of the paper. It should address the research question, the methods, and the conclusions of your analysis.

*"A good recipe for an abstract is: first sentence: specify the general area of the paper and encourage the reader; second sentence: specify the dataset and methods at a general level; third sentence: specify the headline result; and a fourth sentence about implications."*
:::
