---
title: "PC_Bootstrap_Graphs"
author: "Patrick S Connelly"
date: "2023-12-10"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

```{r, include=FALSE}
boot <- read.csv('../data/full_bootstrap_data.csv')

age_lev = factor(
  c("0-2","3-9","10-19","20-29","30-39","40-49","50-59","60-69","70-130")
)

df_bootstrap_data <- boot %>% filter(model=='DeepFace')
ff_bootstrap_data <- boot %>% filter(model=='FairFace')

full_results <- read.csv('../data/combined_p_val_F1_acc.csv')
```


## Single Test Condition Graphs

```{r, echo=FALSE}
#facet-wrapped results from bootstrapping
#age plots
df_bootstrap_data %>% filter(test_prop=='age_bins',test_gender=='All',test_race=='All') %>%
  mutate(test_age=factor(test_age,levels=age_lev)) %>% 
  ggplot()+geom_density(aes(x=value,color=datasource)) + facet_wrap(~test_age) + xlab('sample proportion') + ggtitle('DeepFace vs. Source Age Bootstrap Proportions')
#age test table
full_results %>% filter(
  model=='DeepFace',
  test_prop=='age_bins',
  test_gender=='All',
  test_race=='All'
) %>% 
  select(
    test_prop,
    test_race,
    test_gender,
    test_age,
    model_p_value,
    model_power,
    model_F1,
    model_Accuracy
  ) %>% knitr::kable()

#gender plots
df_bootstrap_data %>% filter(test_prop=='genders',test_age=='All',test_race=='All') %>% ggplot()+geom_density(aes(x=value,color=datasource)) + facet_wrap(~test_gender)+ xlab('sample proportion')+ ggtitle('DeepFace vs. Source Gender Bootstrap Proportions')
#gender test table
full_results %>% filter(
  model=='DeepFace',
  test_prop=='genders',
  test_age=='All',
  test_race=='All'
) %>% 
  select(
    test_prop,
    test_race,
    test_gender,
    test_age,
    model_p_value,
    model_power,
    model_F1,
    model_Accuracy
  ) %>% knitr::kable()

#race plots
df_bootstrap_data %>% filter(test_prop=='races',test_age=='All',test_gender=='All') %>% ggplot()+geom_density(aes(x=value,color=datasource)) + facet_wrap(~test_race)+ xlab('sample proportion')+ ggtitle('DeepFace vs. Source Race Bootstrap Proportions')
#race test table
full_results %>% filter(
  model=='DeepFace',
  test_prop=='races',
  test_gender=='All',
  test_age=='All'
) %>% 
  select(
    test_prop,
    test_race,
    test_gender,
    test_age,
    model_p_value,
    model_power,
    model_F1,
    model_Accuracy
  ) %>% knitr::kable()

#age plots
ff_bootstrap_data %>% filter(test_prop=='age_bins',test_gender=='All',test_race=='All') %>%
  mutate(test_age=factor(test_age,levels=age_lev)) %>% 
  ggplot()+geom_density(aes(x=value,color=datasource)) + facet_wrap(~test_age)+ xlab('sample proportion')+ ggtitle('FairFace vs. Source Age Bootstrap Proportions')
#age test table
full_results %>% filter(
  model=='FairFace',
  test_prop=='age_bins',
  test_gender=='All',
  test_race=='All'
) %>% 
  select(
    test_prop,
    test_race,
    test_gender,
    test_age,
    model_p_value,
    model_power,
    model_F1,
    model_Accuracy
  ) %>% knitr::kable()


#gender plots
ff_bootstrap_data %>% filter(test_prop=='genders',test_age=='All',test_race=='All') %>% ggplot()+geom_density(aes(x=value,color=datasource)) + facet_wrap(~test_gender)+  xlab('sample proportion')+ ggtitle('FairFace vs. Source Gender Bootstrap Proportions')
#gender test table 
full_results %>% filter(
  model=='FairFace',
  test_prop=='genders',
  test_age=='All',
  test_race=='All'
) %>% 
  select(
    test_prop,
    test_race,
    test_gender,
    test_age,
    model_p_value,
    model_power,
    model_F1,
    model_Accuracy
  ) %>% knitr::kable()


#race plots
ff_bootstrap_data %>% filter(test_prop=='races',test_age=='All',test_gender=='All') %>% ggplot()+geom_density(aes(x=value,color=datasource)) + facet_wrap(~test_race)+ xlab('sample proportion')+ ggtitle('FairFace vs. Source Race Bootstrap Proportions')
#race test table
full_results %>% filter(
  model=='DeepFace',
  test_prop=='races',
  test_gender=='All',
  test_age=='All'
) %>% 
  select(
    test_prop,
    test_race,
    test_gender,
    test_age,
    model_p_value,
    model_power,
    model_F1,
    model_Accuracy
  ) %>% knitr::kable()
```

### Race proportions, given Age Group

```{r, echo=FALSE}
df_bootstrap_data %>% filter(test_prop=='races',test_age!='All', test_gender=='All',test_race!='All') %>% mutate(test_age=factor(test_age,levels=age_lev)) %>% 
    ggplot()+
    geom_density(
        aes(x=value,color=datasource)
    )+
    facet_grid(test_age~test_race)+
    ggtitle("DeepFace Race Proportion Predictions, Given Age")

full_results %>% filter(
  model=='DeepFace',
  test_prop=='races',
  test_age!='All',
  test_gender=='All',
  test_race!='All'
) %>% 
  select(
    test_prop,
    test_race,
    test_age,
    model_p_value,
    model_power,
    model_F1,
    model_Accuracy
  ) %>% knitr::kable()

ff_bootstrap_data %>% filter(test_prop=='races',test_age!='All', test_gender=='All',test_race!='All') %>% mutate(test_age=factor(test_age,levels=age_lev)) %>% 
    ggplot()+
    geom_density(
        aes(x=value,color=datasource)
    )+
    facet_grid(test_age~test_race)+
    ggtitle("FairFace Race Proportion Predictions, Given Age")

full_results %>% filter(
  model=='FairFace',
  test_prop=='races',
  test_gender=='All',
  test_race=='All'
) %>% 
  select(
    test_prop,
    test_race,
    test_age,
    model_p_value,
    model_power,
    model_F1,
    model_Accuracy
  ) %>% knitr::kable()
```

### Race proportions, given Gender

```{r, echo=FALSE}
df_bootstrap_data %>% filter(test_prop=='races',test_age=='All', test_gender!='All',test_race!='All') %>% 
    ggplot()+
    geom_density(
        aes(x=value,color=datasource)
    )+
    facet_grid(test_gender~test_race)+
    ggtitle("DeepFace Race Proportion Predictions, Given Gender")

full_results %>% filter(
  model=='DeepFace',
  test_prop=='races',
  test_gender!='All',
  test_race!='All',
  test_age=='All'
) %>% 
  select(
    test_prop,
    test_race,
    test_gender,
    model_p_value,
    model_power,
    model_F1,
    model_Accuracy
  ) %>% knitr::kable()

ff_bootstrap_data %>% filter(test_prop=='races',test_age=='All', test_gender!='All',test_race!='All') %>% 
    ggplot()+
    geom_density(
        aes(x=value,color=datasource)
    )+
    facet_grid(test_gender~test_race)+
    ggtitle("FairFace Race Proportion Predictions, Given Gender")

full_results %>% filter(
  model=='FairFace',
  test_prop=='races',
  test_gender!='All',
  test_race!='All',
  test_age=='All'
) %>% 
  select(
    test_prop,
    test_race,
    test_gender,
    model_p_value,
    model_power,
    model_F1,
    model_Accuracy
  ) %>% knitr::kable()
```

### Age proportions, Given Gender

```{r, echo=FALSE}
df_bootstrap_data %>% filter(test_prop=='age_bins',test_age!='All', test_gender!='All',test_race=='All') %>% 
  mutate(test_age=factor(test_age,levels=age_lev)) %>% 
    ggplot()+
    geom_density(
        aes(x=value,color=datasource)
    )+
    facet_grid(test_gender~test_age)+
    ggtitle("DeepFace Age Proportion Predictions, Given Gender")

full_results %>% filter(
  model=='DeepFace',
  test_prop=='age_bins',
  test_age!='All',
  test_gender!='All',
  test_race=='All'
) %>% 
  select(
    test_prop,
    test_gender,
    test_age,
    model_p_value,
    model_power,
    model_F1,
    model_Accuracy
  ) %>% mutate(test_age=factor(test_age,levels=age_lev))  %>% knitr::kable()


ff_bootstrap_data %>% filter(test_prop=='age_bins',test_age!='All', test_gender!='All',test_race=='All') %>% 
  mutate(test_age=factor(test_age,levels=age_lev)) %>% 
    ggplot()+
    geom_density(
        aes(x=value,color=datasource)
    )+
    facet_grid(test_gender~test_age)+
    ggtitle("FairFace Age Proportion Predictions, Given Gender")

full_results %>% filter(
  model=='FairFace',
  test_prop=='age_bins',
  test_age!='All',
  test_gender!='All',
  test_race=='All'
) %>% 
  select(
    test_prop,
    test_gender,
    test_age,
    model_p_value,
    model_power,
    model_F1,
    model_Accuracy
  ) %>% mutate(test_age=factor(test_age,levels=age_lev))  %>% knitr::kable()
```


### Age Proportions, Given Race

```{r, echo=FALSE}
df_bootstrap_data %>% filter(test_prop=='age_bins',test_age!='All', test_gender=='All',test_race!='All') %>% 
    mutate(test_age=factor(test_age,levels=age_lev)) %>% 
    ggplot()+
    geom_density(
        aes(x=value,color=datasource)
    )+
    facet_grid(test_race~test_age)+
    ggtitle("DeepFace Age Proportion Predictions, Given Race")

full_results %>% filter(
  model=='DeepFace',
  test_prop=='age_bins',
  test_age!='All',
  test_gender=='All',
  test_race!='All'
) %>% 
  select(
    test_prop,
    test_race,
    test_age,
    model_p_value,
    model_power,
    model_F1,
    model_Accuracy
  ) %>% mutate(test_age=factor(test_age,levels=age_lev))  %>% knitr::kable()

ff_bootstrap_data %>% filter(test_prop=='age_bins',test_age!='All', test_gender=='All',test_race!='All') %>% 
    mutate(test_age=factor(test_age,levels=age_lev)) %>% 
    ggplot()+
    geom_density(
        aes(x=value,color=datasource)
    )+
    facet_grid(test_race~test_age)+
    ggtitle("FairFace Age Proportion Predictions, Given Race")


full_results %>% filter(
  model=='FairFace',
  test_prop=='age_bins',
  test_age!='All',
  test_gender=='All',
  test_race!='All'
) %>% 
  select(
    test_prop,
    test_race,
    test_age,
    model_p_value,
    model_power,
    model_F1,
    model_Accuracy
  ) %>% mutate(test_age=factor(test_age,levels=age_lev))  %>% knitr::kable()
```

### Gender Proportions, Given Race

```{r, echo=FALSE}
df_bootstrap_data %>% filter(test_prop=='genders',test_age=='All', test_gender!='All',test_race!='All') %>% 
    ggplot()+
    geom_density(
        aes(x=value,color=datasource)
    )+
    facet_grid(test_race~test_gender)+
    ggtitle("DeepFace Gender Proportion Predictions, Given Race")


full_results %>% filter(
  model=='DeepFace',
  test_prop=='genders',
  test_age=='All',
  test_gender!='All',
  test_race!='All'
) %>% 
  select(
    test_prop,
    test_race,
    test_gender,
    model_p_value,
    model_power,
    model_F1,
    model_Accuracy
  )  %>% knitr::kable()


ff_bootstrap_data %>% filter(test_prop=='genders',test_age=='All', test_gender!='All',test_race!='All') %>% 
    ggplot()+
    geom_density(
        aes(x=value,color=datasource)
    )+
    facet_grid(test_race~test_gender)+
    ggtitle("FairFace Gender Proportion Predictions, Given Race")
full_results %>% filter(
  model=='FairFace',
  test_prop=='genders',
  test_age=='All',
  test_gender!='All',
  test_race!='All'
) %>% 
  select(
    test_prop,
    test_race,
    test_gender,
    model_p_value,
    model_power,
    model_F1,
    model_Accuracy
  ) %>% knitr::kable()

```


### Gender Proportions, Given Age Group

```{r, echo=FALSE}
df_bootstrap_data %>% filter(test_prop=='genders',test_age!='All', test_gender!='All',test_race=='All') %>% 
    mutate(test_age=factor(test_age,levels=age_lev)) %>% 
    ggplot()+
    geom_density(
        aes(x=value,color=datasource)
    )+
    facet_grid(test_age~test_gender)+
    ggtitle("DeepFace Gender Proportion Predictions, Given Age")

full_results %>% filter(
  model=='FairFace',
  test_prop=='genders',
  test_age!='All',
  test_gender!='All',
  test_race=='All'
) %>% 
  select(
    test_prop,
    test_gender,
    test_age,
    model_p_value,
    model_power,
    model_F1,
    model_Accuracy
  )  %>% knitr::kable()


ff_bootstrap_data %>% filter(test_prop=='genders',test_age!='All', test_gender!='All',test_race=='All') %>% 
    mutate(test_age=factor(test_age,levels=age_lev)) %>% 
  
    ggplot()+
    geom_density(
        aes(x=value,color=datasource)
    )+
    facet_grid(test_age~test_gender)+
    ggtitle("FairFace Gender Proportion Predictions, Given Age")

full_results %>% filter(
  model=='DeepFace',
  test_prop=='genders',
  test_age!='All',
  test_gender!='All',
  test_race=='All'
) %>% 
  select(
    test_prop,
    test_gender,
    test_age,
    model_p_value,
    model_power,
    model_F1,
    model_Accuracy
  )  %>% knitr::kable()
```


## Very Detailed Graphs (3 test conditions)

### Racial Groups

#### Proportion of Asian, Given Age and Gender

```{r, echo=FALSE}
df_bootstrap_data %>% filter(test_prop=='races',test_age!='All', test_gender!='All',test_race=='Asian') %>% 
    mutate(test_age=factor(test_age,levels=age_lev)) %>% 
  
    ggplot()+
    geom_density(
        aes(x=value,color=datasource)
    )+
    facet_grid(test_age~test_gender)+
    ggtitle("DeepFace Proportion of Asian, Given Age and Gender")
full_results %>% filter(
  model=='DeepFace',
  test_prop=='races',
  test_age!='All',
  test_gender!='All',
  test_race=='Asian'
) %>% 
  select(
    test_prop,
    test_race,
    test_gender,
    test_age,
    model_p_value,
    model_power,
    model_F1,
    model_Accuracy
  )  %>% knitr::kable()

ff_bootstrap_data %>% filter(test_prop=='races',test_age!='All', test_gender!='All',test_race=='Asian') %>% 
    mutate(test_age=factor(test_age,levels=age_lev)) %>% 
  
    ggplot()+
    geom_density(
        aes(x=value,color=datasource)
    )+
    facet_grid(test_age~test_gender)+
    ggtitle("FairFace Proportion of Asian, Given Age and Gender")

full_results %>% filter(
  model=='FairFace',
  test_prop=='races',
  test_age!='All',
  test_gender!='All',
  test_race=='Asian'
) %>% 
  select(
    test_prop,
    test_race,
    test_gender,
    test_age,
    model_p_value,
    model_power,
    model_F1,
    model_Accuracy
  )  %>% knitr::kable()
```

#### Proportion of Black, Given Age and Gender

```{r, echo=FALSE}
df_bootstrap_data %>% filter(test_prop=='races',test_age!='All', test_gender!='All',test_race=='Black') %>% 
    mutate(test_age=factor(test_age,levels=age_lev)) %>% 
  
    ggplot()+
    geom_density(
        aes(x=value,color=datasource)
    )+
    facet_grid(test_age~test_gender)+
    ggtitle("DeepFace Proportion of Black, Given Age and Gender")
full_results %>% filter(
  model=='DeepFace',
  test_prop=='races',
  test_age!='All',
  test_gender!='All',
  test_race=='Black'
) %>% 
  select(
    test_prop,
    test_race,
    test_gender,
    test_age,
    model_p_value,
    model_power,
    model_F1,
    model_Accuracy
  )  %>% knitr::kable()

ff_bootstrap_data %>% filter(test_prop=='races',test_age!='All', test_gender!='All',test_race=='Black') %>% 
    mutate(test_age=factor(test_age,levels=age_lev)) %>% 
  
    ggplot()+
    geom_density(
        aes(x=value,color=datasource)
    )+
    facet_grid(test_age~test_gender)+
    ggtitle("FairFace Proportion of Black, Given Age and Gender")
full_results %>% filter(
  model=='FairFace',
  test_prop=='races',
  test_age!='All',
  test_gender!='All',
  test_race=='Black'
) %>% 
  select(
    test_prop,
    test_race,
    test_gender,
    test_age,
    model_p_value,
    model_power,
    model_F1,
    model_Accuracy
  )  %>% knitr::kable()

```

#### Proportion of Indian, Given Age and Gender

```{r, echo=FALSE}
df_bootstrap_data %>% filter(test_prop=='races',test_age!='All', test_gender!='All',test_race=='Indian') %>% 
    mutate(test_age=factor(test_age,levels=age_lev)) %>% 
  
    ggplot()+
    geom_density(
        aes(x=value,color=datasource)
    )+
    facet_grid(test_age~test_gender)+
    ggtitle("DeepFace Proportion of Indian, Given Age and Gender")
full_results %>% filter(
  model=='DeepFace',
  test_prop=='races',
  test_age!='All',
  test_gender!='All',
  test_race=='Indian'
) %>% 
  select(
    test_prop,
    test_race,
    test_gender,
    test_age,
    model_p_value,
    model_power,
    model_F1,
    model_Accuracy
  )  %>% knitr::kable()


ff_bootstrap_data %>% filter(test_prop=='races',test_age!='All', test_gender!='All',test_race=='Indian') %>% 
    mutate(test_age=factor(test_age,levels=age_lev)) %>% 
  
    ggplot()+
    geom_density(
        aes(x=value,color=datasource)
    )+
    facet_grid(test_age~test_gender)+
    ggtitle("FairFace Proportion of Indian, Given Age and Gender")
full_results %>% filter(
  model=='FairFace',
  test_prop=='races',
  test_age!='All',
  test_gender!='All',
  test_race=='Indian'
) %>% 
  select(
    test_prop,
    test_race,
    test_gender,
    test_age,
    model_p_value,
    model_power,
    model_F1,
    model_Accuracy
  )  %>% knitr::kable()

```

#### Proportion of Other, Given Age and Gender

```{r, echo=FALSE}
df_bootstrap_data %>% filter(test_prop=='races',test_age!='All', test_gender!='All',test_race=='Other') %>% 
    mutate(test_age=factor(test_age,levels=age_lev)) %>% 
  
    ggplot()+
    geom_density(
        aes(x=value,color=datasource)
    )+
    facet_grid(test_age~test_gender)+
    ggtitle("DeepFace Proportion of Other, Given Age and Gender")
full_results %>% filter(
  model=='DeepFace',
  test_prop=='races',
  test_age!='All',
  test_gender!='All',
  test_race=='Other'
) %>% 
  select(
    test_prop,
    test_race,
    test_gender,
    test_age,
    model_p_value,
    model_power,
    model_F1,
    model_Accuracy
  )  %>% knitr::kable()

ff_bootstrap_data %>% filter(test_prop=='races',test_age!='All', test_gender!='All',test_race=='Other') %>% 
    mutate(test_age=factor(test_age,levels=age_lev)) %>% 
  
    ggplot()+
    geom_density(
        aes(x=value,color=datasource)
    )+
    facet_grid(test_age~test_gender)+
    ggtitle("FairFace Proportion of Other, Given Age and Gender")
full_results %>% filter(
  model=='FairFace',
  test_prop=='races',
  test_age!='All',
  test_gender!='All',
  test_race=='Other'
) %>% 
  select(
    test_prop,
    test_race,
    test_gender,
    test_age,
    model_p_value,
    model_power,
    model_F1,
    model_Accuracy
  )  %>% knitr::kable()

```

#### Proportion of White, Given Age and Gender

```{r, echo=FALSE}

df_bootstrap_data %>% filter(test_prop=='races',test_age!='All', test_gender!='All',test_race=='White') %>% 
    mutate(test_age=factor(test_age,levels=age_lev)) %>% 
  
    ggplot()+
    geom_density(
        aes(x=value,color=datasource)
    )+
    facet_grid(test_age~test_gender)+
    ggtitle("DeepFace Proportion of White, Given Age and Gender")
full_results %>% filter(
  model=='DeepFace',
  test_prop=='races',
  test_age!='All',
  test_gender!='All',
  test_race=='White'
) %>% 
  select(
    test_prop,
    test_race,
    test_gender,
    test_age,
    model_p_value,
    model_power,
    model_F1,
    model_Accuracy
  )  %>% knitr::kable()


ff_bootstrap_data %>% filter(test_prop=='races',test_age!='All', test_gender!='All',test_race=='White') %>% 
    mutate(test_age=factor(test_age,levels=age_lev)) %>% 
  
    ggplot()+
    geom_density(
        aes(x=value,color=datasource)
    )+
    facet_grid(test_age~test_gender)+
    ggtitle("FairFace Proportion of White, Given Age and Gender")
full_results %>% filter(
  model=='FairFace',
  test_prop=='races',
  test_age!='All',
  test_gender!='All',
  test_race=='White'
) %>% 
  select(
    test_prop,
    test_race,
    test_gender,
    test_age,
    model_p_value,
    model_power,
    model_F1,
    model_Accuracy
  )  %>% knitr::kable()
```

### Genders

#### Proportion of Female, Given Race and Age

```{r, echo=FALSE}

df_bootstrap_data %>% filter(test_prop=='genders',test_age!='All', test_gender=='Female',test_race!='All') %>% 
    mutate(test_age=factor(test_age,levels=age_lev)) %>% 
  
    ggplot()+
    geom_density(
        aes(x=value,color=datasource)
    )+
    facet_grid(test_race~test_age)+
    ggtitle("DeepFace Proportion of Female, Given Age and Race")
full_results %>% filter(
  model=='DeepFace',
  test_prop=='genders',
  test_age!='All',
  test_gender=='Female',
  test_race!='All'
) %>% 
  select(
    test_prop,
    test_race,
    test_gender,
    test_age,
    model_p_value,
    model_power,
    model_F1,
    model_Accuracy
  )  %>% knitr::kable()

ff_bootstrap_data %>% filter(test_prop=='genders',test_age!='All', test_gender=='Female',test_race!='All') %>% 
    mutate(test_age=factor(test_age,levels=age_lev)) %>% 
  
    ggplot()+
    geom_density(
        aes(x=value,color=datasource)
    )+
    facet_grid(test_race~test_age)+
    ggtitle("FairFace Proportion of Female, Given Age and Race")

full_results %>% filter(
  model=='FairFace',
  test_prop=='genders',
  test_age!='All',
  test_gender=='Female',
  test_race!='All'
) %>% 
  select(
    test_prop,
    test_race,
    test_gender,
    test_age,
    model_p_value,
    model_power,
    model_F1,
    model_Accuracy
  )  %>% knitr::kable()
```

#### Proportion of Male, Given Race and Age

```{r, echo=FALSE}


df_bootstrap_data %>% filter(test_prop=='genders',test_age!='All', test_gender=='Male',test_race!='All') %>% 
    mutate(test_age=factor(test_age,levels=age_lev)) %>% 
  
    ggplot()+
    geom_density(
        aes(x=value,color=datasource)
    )+
    facet_grid(test_race~test_age)+
    ggtitle("DeepFace Proportion of Male, Given Age and Race")
full_results %>% filter(
  model=='DeepFace',
  test_prop=='genders',
  test_age!='All',
  test_gender=='Male',
  test_race!='All'
) %>% 
  select(
    test_prop,
    test_race,
    test_gender,
    test_age,
    model_p_value,
    model_power,
    model_F1,
    model_Accuracy
  )  %>% knitr::kable()


# 
ff_bootstrap_data %>% filter(test_prop=='genders',test_age!='All', test_gender=='Male',test_race!='All') %>%
    mutate(test_age=factor(test_age,levels=age_lev)) %>%

    ggplot()+
    geom_density(
        aes(x=value,color=datasource)
    )+
    facet_grid(test_race~test_age)+
    ggtitle("FairFace Proportion of Male, Given Age and Race")
full_results %>% filter(
  model=='FairFace',
  test_prop=='genders',
  test_age!='All',
  test_gender=='Male',
  test_race!='All'
) %>% 
  select(
    test_prop,
    test_race,
    test_gender,
    test_age,
    model_p_value,
    model_power,
    model_F1,
    model_Accuracy
  )  %>% knitr::kable()

```


### Age Groups

#### Proportion of 0-2, given gender and race

```{r, echo=FALSE}
df_bootstrap_data %>% filter(test_prop=='age_bins',test_age=='0-2', test_gender!='All',test_race!='All') %>% 
    mutate(test_age=factor(test_age,levels=age_lev)) %>% 
  
    ggplot()+
    geom_density(
        aes(x=value,color=datasource)
    )+
    facet_grid(test_gender~test_race)+
    ggtitle("DeepFace Proportion of 0-2, Given Gender and Race")

full_results %>% filter(
  model=='DeepFace',
  test_prop=='age_bins',
  test_age=='0-2',
  test_gender!='All',
  test_race!='All'
) %>% 
  select(
    test_prop,
    test_race,
    test_gender,
    test_age,
    model_p_value,
    model_power,
    model_F1,
    model_Accuracy
  )  %>% knitr::kable()
# 
ff_bootstrap_data %>% filter(test_prop=='age_bins',test_age=='0-2', test_gender!='All',test_race!='All') %>%
    mutate(test_age=factor(test_age,levels=age_lev)) %>%

    ggplot()+
    geom_density(
        aes(x=value,color=datasource)
    )+
    facet_grid(test_gender~test_race)+
    ggtitle("FairFace Proportion of 0-2, Given Gender and Race")
full_results %>% filter(
  model=='FairFace',
  test_prop=='age_bins',
  test_age=='0-2',
  test_gender!='All',
  test_race!='All'
) %>% 
  select(
    test_prop,
    test_race,
    test_gender,
    test_age,
    model_p_value,
    model_power,
    model_F1,
    model_Accuracy
  )  %>% knitr::kable()
```

#### Proportion of 3-9, given gender and race

```{r, echo=FALSE}

df_bootstrap_data %>% filter(test_prop=='age_bins',test_age=='3-9', test_gender!='All',test_race!='All') %>% 
    mutate(test_age=factor(test_age,levels=age_lev)) %>% 
  
    ggplot()+
    geom_density(
        aes(x=value,color=datasource)
    )+
    facet_grid(test_gender~test_race)+
    ggtitle("DeepFace Proportion of 3-9, Given Gender and Race")

full_results %>% filter(
  model=='DeepFace',
  test_prop=='age_bins',
  test_age=='3-9',
  test_gender!='All',
  test_race!='All'
) %>% 
  select(
    test_prop,
    test_race,
    test_gender,
    test_age,
    model_p_value,
    model_power,
    model_F1,
    model_Accuracy
  )  %>% knitr::kable()

# 
ff_bootstrap_data %>% filter(test_prop=='age_bins',test_age=='3-9', test_gender!='All',test_race!='All') %>%
    mutate(test_age=factor(test_age,levels=age_lev)) %>%

    ggplot()+
    geom_density(
        aes(x=value,color=datasource)
    )+
    facet_grid(test_gender~test_race)+
    ggtitle("FairFace Proportion of 3-9, Given Gender and Race")

full_results %>% filter(
  model=='FairFace',
  test_prop=='age_bins',
  test_age=='3-9',
  test_gender!='All',
  test_race!='All'
) %>% 
  select(
    test_prop,
    test_race,
    test_gender,
    test_age,
    model_p_value,
    model_power,
    model_F1,
    model_Accuracy
  )  %>% knitr::kable()
```


#### Proportion of 10-19, given gender and race

```{r, echo=FALSE}

df_bootstrap_data %>% filter(test_prop=='age_bins',test_age=='10-19', test_gender!='All',test_race!='All') %>% 
    mutate(test_age=factor(test_age,levels=age_lev)) %>% 
  
    ggplot()+
    geom_density(
        aes(x=value,color=datasource)
    )+
    facet_grid(test_gender~test_race)+
    ggtitle("DeepFace Proportion of 10-19, Given Gender and Race")
full_results %>% filter(
  model=='DeepFace',
  test_prop=='age_bins',
  test_age=='10-19',
  test_gender!='All',
  test_race!='All'
) %>% 
  select(
    test_prop,
    test_race,
    test_gender,
    test_age,
    model_p_value,
    model_power,
    model_F1,
    model_Accuracy
  )  %>% knitr::kable()

# 
ff_bootstrap_data %>% filter(test_prop=='age_bins',test_age=='10-19', test_gender!='All',test_race!='All') %>%
    mutate(test_age=factor(test_age,levels=age_lev)) %>%

    ggplot()+
    geom_density(
        aes(x=value,color=datasource)
    )+
    facet_grid(test_gender~test_race)+
    ggtitle("FairFace Proportion of 10-19, Given Gender and Race")
full_results %>% filter(
  model=='FairFace',
  test_prop=='age_bins',
  test_age=='10-19',
  test_gender!='All',
  test_race!='All'
) %>% 
  select(
    test_prop,
    test_race,
    test_gender,
    test_age,
    model_p_value,
    model_power,
    model_F1,
    model_Accuracy
  )  %>% knitr::kable()
```


#### Proportion of 20-29, given gender and race

```{r, echo=FALSE}

df_bootstrap_data %>% filter(test_prop=='age_bins',test_age=='20-29', test_gender!='All',test_race!='All') %>% 
    mutate(test_age=factor(test_age,levels=age_lev)) %>% 
  
    ggplot()+
    geom_density(
        aes(x=value,color=datasource)
    )+
    facet_grid(test_gender~test_race)+
    ggtitle("DeepFace Proportion of 20-29, Given Gender and Race")

full_results %>% filter(
  model=='DeepFace',
  test_prop=='age_bins',
  test_age=='20-29',
  test_gender!='All',
  test_race!='All'
) %>% 
  select(
    test_prop,
    test_race,
    test_gender,
    test_age,
    model_p_value,
    model_power,
    model_F1,
    model_Accuracy
  )  %>% knitr::kable()

# 
ff_bootstrap_data %>% filter(test_prop=='age_bins',test_age=='20-29', test_gender!='All',test_race!='All') %>%
    mutate(test_age=factor(test_age,levels=age_lev)) %>%

    ggplot()+
    geom_density(
        aes(x=value,color=datasource)
    )+
    facet_grid(test_gender~test_race)+
    ggtitle("FairFace Proportion of 20-29, Given Gender and Race")

full_results %>% filter(
  model=='FairFace',
  test_prop=='age_bins',
  test_age=='20-29',
  test_gender!='All',
  test_race!='All'
) %>% 
  select(
    test_prop,
    test_race,
    test_gender,
    test_age,
    model_p_value,
    model_power,
    model_F1,
    model_Accuracy
  )  %>% knitr::kable()
```


#### Proportion of 30-39, given gender and race

```{r, echo=FALSE}

df_bootstrap_data %>% filter(test_prop=='age_bins',test_age=='30-39', test_gender!='All',test_race!='All') %>% 
    mutate(test_age=factor(test_age,levels=age_lev)) %>% 
  
    ggplot()+
    geom_density(
        aes(x=value,color=datasource)
    )+
    facet_grid(test_gender~test_race)+
    ggtitle("DeepFace Proportion of 30-39, Given Gender and Race")
full_results %>% filter(
  model=='DeepFace',
  test_prop=='age_bins',
  test_age=='30-39',
  test_gender!='All',
  test_race!='All'
) %>% 
  select(
    test_prop,
    test_race,
    test_gender,
    test_age,
    model_p_value,
    model_power,
    model_F1,
    model_Accuracy
  )  %>% knitr::kable()
# 
ff_bootstrap_data %>% filter(test_prop=='age_bins',test_age=='30-39', test_gender!='All',test_race!='All') %>%
    mutate(test_age=factor(test_age,levels=age_lev)) %>%

    ggplot()+
    geom_density(
        aes(x=value,color=datasource)
    )+
    facet_grid(test_gender~test_race)+
    ggtitle("FairFace Proportion of 30-39, Given Gender and Race")
full_results %>% filter(
  model=='FairFace',
  test_prop=='age_bins',
  test_age=='30-39',
  test_gender!='All',
  test_race!='All'
) %>% 
  select(
    test_prop,
    test_race,
    test_gender,
    test_age,
    model_p_value,
    model_power,
    model_F1,
    model_Accuracy
  )  %>% knitr::kable()
```


#### Proportion of 40-49, given gender and race

```{r, echo=FALSE}

df_bootstrap_data %>% filter(test_prop=='age_bins',test_age=='40-49', test_gender!='All',test_race!='All') %>% 
    mutate(test_age=factor(test_age,levels=age_lev)) %>% 
  
    ggplot()+
    geom_density(
        aes(x=value,color=datasource)
    )+
    facet_grid(test_gender~test_race)+
    ggtitle("DeepFace Proportion of 40-49, Given Gender and Race")

full_results %>% filter(
  model=='DeepFace',
  test_prop=='age_bins',
  test_age=='40-49',
  test_gender!='All',
  test_race!='All'
) %>% 
  select(
    test_prop,
    test_race,
    test_gender,
    test_age,
    model_p_value,
    model_power,
    model_F1,
    model_Accuracy
  )  %>% knitr::kable()

# 
ff_bootstrap_data %>% filter(test_prop=='age_bins',test_age=='40-49', test_gender!='All',test_race!='All') %>%
    mutate(test_age=factor(test_age,levels=age_lev)) %>%

    ggplot()+
    geom_density(
        aes(x=value,color=datasource)
    )+
    facet_grid(test_gender~test_race)+
    ggtitle("FairFace Proportion of 40-49, Given Gender and Race")
full_results %>% filter(
  model=='FairFace',
  test_prop=='age_bins',
  test_age=='40-49',
  test_gender!='All',
  test_race!='All'
) %>% 
  select(
    test_prop,
    test_race,
    test_gender,
    test_age,
    model_p_value,
    model_power,
    model_F1,
    model_Accuracy
  )  %>% knitr::kable()
```

#### Proportion of 50-59, given gender and race

```{r, echo=FALSE}

df_bootstrap_data %>% filter(test_prop=='age_bins',test_age=='50-59', test_gender!='All',test_race!='All') %>% 
    mutate(test_age=factor(test_age,levels=age_lev)) %>% 
  
    ggplot()+
    geom_density(
        aes(x=value,color=datasource)
    )+
    facet_grid(test_gender~test_race)+
    ggtitle("DeepFace Proportion of 50-59, Given Gender and Race")

full_results %>% filter(
  model=='DeepFace',
  test_prop=='age_bins',
  test_age=='50-59',
  test_gender!='All',
  test_race!='All'
) %>% 
  select(
    test_prop,
    test_race,
    test_gender,
    test_age,
    model_p_value,
    model_power,
    model_F1,
    model_Accuracy
  )  %>% knitr::kable()

# 
ff_bootstrap_data %>% filter(test_prop=='age_bins',test_age=='50-59', test_gender!='All',test_race!='All') %>%
    mutate(test_age=factor(test_age,levels=age_lev)) %>%

    ggplot()+
    geom_density(
        aes(x=value,color=datasource)
    )+
    facet_grid(test_gender~test_race)+
    ggtitle("FairFace Proportion of 50-59, Given Gender and Race")
full_results %>% filter(
  model=='FairFace',
  test_prop=='age_bins',
  test_age=='50-59',
  test_gender!='All',
  test_race!='All'
) %>% 
  select(
    test_prop,
    test_race,
    test_gender,
    test_age,
    model_p_value,
    model_power,
    model_F1,
    model_Accuracy
  )  %>% knitr::kable()
```

#### Proportion of 60-69, given gender and race

```{r, echo=FALSE}

df_bootstrap_data %>% filter(test_prop=='age_bins',test_age=='60-69', test_gender!='All',test_race!='All') %>% 
    mutate(test_age=factor(test_age,levels=age_lev)) %>% 
  
    ggplot()+
    geom_density(
        aes(x=value,color=datasource)
    )+
    facet_grid(test_gender~test_race)+
    ggtitle("DeepFace Proportion of 60-69, Given Gender and Race")
full_results %>% filter(
  model=='DeepFace',
  test_prop=='age_bins',
  test_age=='60-69',
  test_gender!='All',
  test_race!='All'
) %>% 
  select(
    test_prop,
    test_race,
    test_gender,
    test_age,
    model_p_value,
    model_power,
    model_F1,
    model_Accuracy
  )  %>% knitr::kable()

# 
ff_bootstrap_data %>% filter(test_prop=='age_bins',test_age=='60-69', test_gender!='All',test_race!='All') %>%
    mutate(test_age=factor(test_age,levels=age_lev)) %>%

    ggplot()+
    geom_density(
        aes(x=value,color=datasource)
    )+
    facet_grid(test_gender~test_race)+
    ggtitle("FairFace Proportion of 60-69, Given Gender and Race")
full_results %>% filter(
  model=='FairFace',
  test_prop=='age_bins',
  test_age=='60-69',
  test_gender!='All',
  test_race!='All'
) %>% 
  select(
    test_prop,
    test_race,
    test_gender,
    test_age,
    model_p_value,
    model_power,
    model_F1,
    model_Accuracy
  )  %>% knitr::kable()
```

#### Proportion of 70-130, given gender and race

```{r, echo=FALSE}

df_bootstrap_data %>% filter(test_prop=='age_bins',test_age=='70-130', test_gender!='All',test_race!='All') %>% 
    mutate(test_age=factor(test_age,levels=age_lev)) %>% 
  
    ggplot()+
    geom_density(
        aes(x=value,color=datasource)
    )+
    facet_grid(test_gender~test_race)+
    ggtitle("DeepFace Proportion of 70-130, Given Gender and Race")
full_results %>% filter(
  model=='DeepFace',
  test_prop=='age_bins',
  test_age=='70-130',
  test_gender!='All',
  test_race!='All'
) %>% 
  select(
    test_prop,
    test_race,
    test_gender,
    test_age,
    model_p_value,
    model_power,
    model_F1,
    model_Accuracy
  )  %>% knitr::kable()

# 
ff_bootstrap_data %>% filter(test_prop=='age_bins',test_age=='70-130', test_gender!='All',test_race!='All') %>%
    mutate(test_age=factor(test_age,levels=age_lev)) %>%

    ggplot()+
    geom_density(
        aes(x=value,color=datasource)
    )+
    facet_grid(test_gender~test_race)+
    ggtitle("FairFace Proportion of 70-130, Given Gender and Race")
full_results %>% filter(
  model=='FairFace',
  test_prop=='age_bins',
  test_age=='70-130',
  test_gender!='All',
  test_race!='All'
) %>% 
  select(
    test_prop,
    test_race,
    test_gender,
    test_age,
    model_p_value,
    model_power,
    model_F1,
    model_Accuracy
  ) %>% knitr::kable()
```
